\subsection{Examiner 1: Dr. Makarand Tapaswi - IIITH317}
Overall Evaluation: {\bf Suitable for MS}
\begin{quote}
    Extremely well written chapters 1 introduction and 2 foundation
    model; well done! \\
    Just 3 comments:
    \begin{enumerate}
        \item Paragraph before 3.2.1.3, Process, you mention selecting
            facet and layer based on inspection, but should rather be
            based on ablations (Fig 3.4) right?
        \item I missed one analysis; given the aggregated features, do
            the results change based on how the distances or
            similarities are computed between query and db images? How
            is this done currently?
        \item Table 3.8, and some other places, sometimes the
            comparison is unfair. ViT-G is a huge model, comparing it
            with ViT-B CosPlace and saying it's better would be
            expected right?
    \end{enumerate}
    Can discuss these points during the defense, thanks
\end{quote}

\subsection{Examiner 2: Dr. Girish Varma - IIITH245}
Overall Evaluation: {\bf May Accept}
\begin{quote}
    \begin{enumerate}
        \item The thesis is poorly written. The continuity in reading
            the text is lacking.
        \item The problem needs to be more clearly defined. What is
            the input? What is the expected output? What is the metric
            used?
        \item The thesis claims to suggest that they have build a
            "Universal VPR system". Its important also to mention
            where the model fails.
        \item There need to be a clear description why the model could
            be called a foundation model. What does it meant to be a
            foundation model for IR?? The database of the IR is always
            going to be limited and cannot contain all the possible
            images of the world? Foundation models are supposed to
            work without any modifications on a wide variety of
            scenarios (without even retraining). Its unclear in what
            sense the term is being used.
        \item Why is a detailed survey of SLAM needed when the focus
            of the thesis is VPR or IR??
        \item In table 3.8, 3.9 it is not mentioned what the units for
            the numbers are or what metric is being talked about.
    \end{enumerate}
    Please address all these comments before the defense.
\end{quote}
\subsubsection{Additional Comments}
Received through email with subject line ``Re: Thesis Examiner
Comments'' on Saturday, 8\textsuperscript{th} July 2024.
\begin{quote}
    \begin{enumerate}
        \setcounter{enumi}{6}
        \item I expect a very clearly spelt out
            definition/justification about what is meant by a
            Foundation Model for IR and why your model deserves that
            tag, in the thesis. This need to be laid properly in a few
            pages with minimal jargon.
        \item Also, if you are focusing of IR/VPR having a long survey
            on SLAM in the thesis doesn't make sense.
    \end{enumerate}
\end{quote}
