% !TEX root = ./main.tex


I would like to express my deepest gratitude to my supervisor, Dr.
Madhava Krishna. His constant support and encouragement were
invaluable at every step of this journey.  His guidance on mobile
robotics systems, SLAM, local feature methods, and related fields
during the initial stages of the project proved particularly helpful.
This work required significant resources (compute and time) and I
thank him again to provide me with those.

I am equally grateful to my co-advisors, Sourav Garg and Krishna
Murthy.  Sourav Garg's expertise in local features and VPR systems was
instrumental in shaping the technical direction of this work. Krishna
Murthy's insightful brainstorming sessions and critical reviews
greatly improved the quality of my research. 

My sincere thanks to Nikhil Varma Keetha for leading this project.
His clear guidance in assigning tasks and his willingness to expose me
to the fascinating world of research helped me grow immensely as a
researcher. I would also like to thank Jay Karhade for his significant
contributions to the project's success, particularly his work on the
website, dataloaders, and help in benchmarking. I thank their guide
at CMU AirLab, Sebastian Scherer, for letting me collaborate on this
amazing journey.

I would also like to thank staff at RRC and the IIIT Hyderabad
ecosystem. Special thanks to Dr. Semparithi Aravindan for maintaining
our HPC cluster Ada and to promptly help me with my queries. I owe a
lot of my systems knowledge to him. I would also like to thank various
organizations like GitHub, Microsoft, GNU Foundation, DuckDuckGo,
Google, etc. without whose tools none of this work would be possible.

Finally, I would like to thank my mother, father, and sister, for
supporting me throughout my entire life and particularly during my
master's degree. It is because of their unconditional love and prayers
that I stand where I am today. Lastly, I would thank God for the 
opportunities given to me.
